Crossing Origins by Crossing Formats

### 2012-12-03 main.tex
tweaks

\subsection{Alexa top 100}

A study to evaluate the prevalence of these issues was performed, 
covering the Alexa top 100 websites. Because of their dominance 
on the web, these websites are also the most exposed to security threats.
The study covers PDF-based polyglot attacks using syntax injection as the infiltration method.
The study did not cover polyglot attacks based on content smuggling, as 
potential targets generally require authentication before submitting content.

The study was conducted by supplying the websites with small benign samples 
of PDF syntax, containing keywords and tokens, and examining the responses 
for said tokens. The samples were benign strings containing  The conclusion is 
that nine websites out of the hundred apply insufficient content filtering with 
respect to the PDF format, which have the potential of compromising the 
confidentiality and integrity of the website's users.

>>>>

\subsection{Alexa top 100}
We have conducted a
study to evaluate the prevalence of the problem on popular sites, 
covering the Alexa top 100 websites. Because of their dominance 
on the web, these websites are also the most exposed to security threats.
The study covers PDF-based polyglot attacks using syntax injection as the infiltration method.
It does not involve polyglot attacks based on content smuggling, as 
potential targets generally require authentication before submitting content.

The study is based on supplying the websites with small benign samples 
of PDF syntax, containing keywords and tokens, and examining the responses 
for said tokens. The samples are benign strings containing \todo{?}. The conclusion is 
that nine websites out of the hundred apply insufficient content filtering with 
respect to the PDF format, which have the potential of compromising the 
confidentiality and integrity of the website's users.
%
We are in contact with the teams responsible for the websites to help
mitigate the vulnerabilities.
